\tool: Revisiting BadUSB with Type-C

### 2021-03-07 WOOT/BadUSBC.tex
fuck me with acronyms please

@@

The security of USB protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, USB
    security has caused serious problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising normal USB devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of user interface to conduct precise attacks as well as get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new features of USB Type-C and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing USB Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

@@

>>>>

\newacro{USB}{Universal Serial Bus}
\newacro{HID}{Human Interface Device}
\newacro{UI}{User Interface}
\newacro{PnP}{Plug-and-Play}
\newacro{OEM}{Original Equipment Manufacturer}
\newacro{DoS}{Denial of Service}
\newacro{MHL}{Mobile High-Definition Link}
\newacro{URB}{USB Request Block}
\newacro{OCR}{Optical Character Recognition}
\newacro{GUI}{Graphical User Interface}

@@

The security of \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused serious problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising normal \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of user interface to conduct precise attacks as well as get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new features of \ac{USB} Type-C and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

@@

\acresetall

### 2021-03-07 WOOT/Files/background.tex
fuck me with acronyms please

We first introduce the development of USB specification and emphasize the key
points adopted in this work. We also organized a brief timeline for introducing
key points of each protocol in Table~\ref{table:usb_timeline}.

%\noindent\outline{USB1.x}\\
Proposed in 1996, USB 1.0~\cite{usb10} was developed to provide a unified
interface and thus reducing the cost of reconfiguring the software. It is
worth mentioning that as a polled-bus interface, all data transfers are
initiated by the host.

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of USB 1.0, a standard named HID (Human
Interface Device)~\cite{hid} was born based on USB. HID is
designed with to unify the implementation for devices like mice,
keyboards, etc. Before its appearance, the standard is divided between
manufacturers, for example, the mouse of Company A may use X-Y coordinates to
represent its location while the mouse of Company B uses relative displacement.
This means every device needs its own driver to work. After HID, users only need to
write one driver for an entire class of HIDs. Furthermore, HID standard also
requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed
convenient but insecure too.

In 1998, the first widely supported USB protocol was born. USB1.1~\cite{usb11}
provided two data transfer rates which are low speed (1.5 Mbit/s) and full
speed (12 MBit/s). At this point, due to the transfer limit, it only supports
limited types of devices like keyboards, mice, etc.

%\noindent\outline{USB2.0}\\
In 2000, USB 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards were
supported in this revision. Such a high data transfer rate also gave rise to the
popularity of ``flash drive'', a portable device that allows physically
transferring data around~\cite{sok}. Though various peripherals were supported
in USB 2.0, there was no reliable way to identify the type of device. This
security flaw allowed attacks like BadUSB~\cite{badusb,rubber}.

%\noindent\outline{USB3.x}\\
USB 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
transfer rate. Like its predecessor, more classes of peripherals were supported
in this revision. In 2013, the USB Type-C connector standard was introduced as a
part of USB 3.1~\cite{usb31}, providing a unified connector type for
PowerDelivery (PD), Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
security was introduced in 3.x revisions, meaning any device claiming
itself as a monitor can capture the video stream from the host. Exposing
such a multi-propose connector unprotected is insecure and allows attacks like
this work \tool. In 2017, USB 3.2~\cite{usb32} was released, doubling the data
transfer rate (20 Gbit/s).

%\noindent\outline{Connector Standard}
\begin{figure}[t]
    \centering
	\includegraphics[width=0.7\linewidth]{./Figs/usb_conn.png}
	\caption{USB 1.x \& 2.x Connector.}
	\label{fig:usb_conn}
\end{figure}

As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x
connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support for
peripherals like DisplayPort \mbox{(10.8 Gbit/s Min)}. Apart from that, support for
other peripherals also require dedicated transferring lane as their standards
are not compatible with USB in most cases.

\begin{figure}[t] 
	\centering
	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} 
	\caption{USB Type-C Connector.} 
	\label{fig:usb_c_conn} 
\end{figure}

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
D-)}. The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers USB packets.

%\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered. As
the USB-IF believes it is the duty of original equipment manufacturers \mbox{(OEMs)}
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

%\fengwei{FIXME: add a reference for each attack in the Table.}
%\fengwei{FIXME: The table is too wide, exceeds the max size.}
\begin{table*}
\begin{tabular}{|c|l|c|c|c|}
	\hline
	\textbf{Year} & \textbf{Protocol Version} & \textbf{Supported Peripherals} & \textbf{Transfer Speed} & \textbf{Attacks} \\
	\hline
	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating (BadUSB)~\cite{badusb} \\
	\hline
	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
	\hline
	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
	\hline
	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
	\hline
	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{USB Protocol Timeline.}
\label{table:usb_timeline}
\end{table*}

>>>>

We first introduce the development of \ac{USB} specification and emphasize the key
points adopted in this work. We also organized a brief timeline for introducing
key points of each protocol in Table~\ref{table:usb_timeline}.

%\noindent\outline{USB1.x}\\
Proposed in 1996, \ac{USB} 1.0~\cite{usb10} was developed to provide a unified
interface and thus reducing the cost of reconfiguring the software. It is
worth mentioning that as a polled-bus interface, all data transfers are
initiated by the host.

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was born based on \ac{USB}. \ac{HID} is
designed with to unify the implementation for devices like mice,
keyboards, etc. Before its appearance, the standard is divided between
manufacturers, for example, the mouse of Company A may use X-Y coordinates to
represent its location while the mouse of Company B uses relative displacement.
This means every device needs its own driver to work. After \ac{HID}, users only need to
write one driver for an entire class of \acs{HID}. Furthermore, \ac{HID} standard also
requires all devices to be \ac{PnP}, which is indeed
convenient but insecure too.

In 1998, the first widely supported \ac{USB} protocol was born. \ac{USB} 1.1~\cite{usb11}
provided two data transfer rates which are low speed (1.5 Mbit/s) and full
speed (12 MBit/s). At this point, due to the transfer limit, it only supports
limited types of devices like keyboards, mice, etc.

%\noindent\outline{USB2.0}\\
In 2000, \ac{USB} 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards were
supported in this revision. Such a high data transfer rate also gave rise to the
popularity of ``flash drive'', a portable device that allows physically
transferring data around~\cite{sok}. Though various peripherals were supported
in \ac{USB} 2.0, there was no reliable way to identify the type of device. This
security flaw allowed attacks like BadUSB~\cite{badusb,rubber}.

%\noindent\outline{USB3.x}\\
\ac{USB} 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
transfer rate. Like its predecessor, more classes of peripherals were supported
in this revision. In 2013, the \ac{USB} Type-C connector standard was introduced as a
part of \ac{USB} 3.1~\cite{usb31}, providing a unified connector type for
PowerDelivery, Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
security was introduced in 3.x revisions, meaning any device claiming
itself as a monitor can capture the video stream from the host. Exposing
such a multi-propose connector unprotected is insecure and allows attacks like
this work \tool. In 2017, \ac{USB} 3.2~\cite{usb32} was released, doubling the data
transfer rate (20 Gbit/s).

%\noindent\outline{Connector Standard}
\begin{figure}[t]
    \centering
	\includegraphics[width=0.7\linewidth]{./Figs/usb_conn.png}
	\caption{\ac{USB} 1.x \& 2.x Connector.}
	\label{fig:usb_conn}
\end{figure}

As illustrated in Figure~\ref{fig:usb_conn}, the original \ac{USB} 1.x \& 2.x
connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support for
peripherals like DisplayPort \mbox{(10.8 Gbit/s Min)}. Apart from that, support for
other peripherals also require dedicated transferring lane as their standards
are not compatible with \ac{USB} in most cases.

\begin{figure}[t] 
	\centering
	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} 
	\caption{\ac{USB} Type-C Connector.} 
	\label{fig:usb_c_conn} 
\end{figure}

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called \ac{USB} Type-C~\cite{typec} is introduced in 2013 by \ac{USB}-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the \ac{USB} 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
D-)}. The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers \ac{USB} packets.

%\noindent\outline{Security Problem}\\
During the development of \ac{USB} specification, security was rarely considered. As
the \ac{USB}-IF believes it is the duty of \acp{OEM}
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

%\fengwei{FIXME: add a reference for each attack in the Table.}
%\fengwei{FIXME: The table is too wide, exceeds the max size.}
\begin{table*}
\begin{tabular}{|c|l|c|c|c|}
	\hline
	\textbf{Year} & \textbf{Protocol Version} & \textbf{Supported Peripherals} & \textbf{Transfer Speed} & \textbf{Attacks} \\
	\hline
	1996 & \ac{USB} 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & \ac{HID} Emulating (BadUSB)~\cite{badusb} \\
	\hline
	2000 & \ac{USB} 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
	\hline
	2008 & \ac{USB} 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
	\hline
	2013 & \ac{USB} 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
	\hline
	2017 & \ac{USB} 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{\ac{USB} Protocol Timeline.}
\label{table:usb_timeline}
\end{table*}

### 2021-03-07 WOOT/Files/badusb.tex
fuck me with acronyms please

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking USB device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we neglect the
effect of notifications from USB devices, as users may not have the knowledge to fully understand such notifications. In
fact, during our experiment, no device had security notifications raised about
suspicious USB devices and only mobile devices had raised a charging notification
about our \tool, which may not be a sufficient warning for users.

We also assume the victim's device is equipped with fully functional USB 3.x
protocol and USB Type-C connector. As the USB 3.x standard is
common nowadays, this assumption can be fulfilled in recent
devices.

@@

As introduced in Section~\ref{sec:related_work},
existing works~\cite{rubber,badusb,
rubberducky2020,usbbypassing,iseeyou,usbdriver} focus on BadUSB attacks.
Many of these take advantage of the \textit{trust-by-default} policy of PC,
pretend to be normal HID devices and utilize USB protocol to perform attacks.
However, these attacks suffer from various drawbacks: \ding{182} attackers can
only simulate limited types of devices such as HIDs (like keyboards and mice)
and disks, which makes the attacks less effective; \ding{183} accurate attacks
could not be performed due to lack of user interface (UI) status. Whatever HID the
attackers simulate their USB devices to be, they could not obtain the UI to
check the status information, which makes it nearly impossible to carry out
their attacks precisely or know the effects after attacks.

@@

In this work, we utilize the new features of USB 3.x~\cite{usb31,usb32} to
address the problem above.  Benefiting from the latest protocol, we simulate
external display and thus obtain the video stream to perform accurate
attacks. However, we still unable to bypass defenses like GoodUSB~\cite{tian2015defending}, which completely blocks unauthorized functionality. This will be further discussed in Section~\ref{sec:discussion}

@@

%\fengwei{We need to
%explain the figure. What are the boxes? Where is victim? Where is the attacker?
%The list below only shows the internal components in the malicious USB device.
%We might also consider to explain this in the Figure caption.}

@@

	\item\underline{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port, etc.

@@

	\item\underline{HID Emulator} emulates HID device which can be controlled from the attacker.

	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via HID Emulator.

@@

\textbf{HID Emulation Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
send constructed HID packet to the victim. These constructed HID packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using USB 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such feedback channel largely strengthen the attack ability of \tool.

Moreover, as the mouse relies on the visual feedback to work properly, its
emulation and automation were not supported by the original version of BadUSB.
Yet with the video output support from USB 3.x, our \tool implements a
full-functional mouse emulation. This function enables attacks toward pure GUI
programs and shows attacks in the mobile attack scenarios. Details can
be obtained in Section~\ref{sec:experiment}.

@@

\textbf{Video Capture Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

@@

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only
the victim's device treat \tool as an external display, but also a valid HID
input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirect it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movement from the attacker
through GSM/WiFi and replays them to the victim by the USB emulation.

>>>>

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we neglect the
effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
fact, during our experiment, no device had security notifications raised about
suspicious \ac{USB} devices and only mobile devices had raised a charging notification
about our \tool, which may not be a sufficient warning for users.

We also assume the victim's device is equipped with fully functional \ac{USB} 3.x
protocol and \ac{USB} Type-C connector. As the \ac{USB} 3.x standard is
common nowadays, this assumption can be fulfilled in recent
devices.

@@

As introduced in Section~\ref{sec:related_work},
existing works~\cite{rubber,badusb,
rubberducky2020,usbbypassing,iseeyou,usbdriver} focus on BadUSB attacks.
Many of these take advantage of the \textit{trust-by-default} policy of PC,
pretend to be normal \ac{HID} devices and utilize \ac{USB} protocol to perform attacks.
However, these attacks suffer from various drawbacks: \ding{182} attackers can
only simulate limited types of devices such as \acp{HID} (like keyboards and mice)
and disks, which makes the attacks less effective; \ding{183} accurate attacks
could not be performed due to lack of \ac{UI} status. Whatever \ac{HID} the
attackers simulate their \ac{USB} devices to be, they could not obtain the \ac{UI} to
check the status information, which makes it nearly impossible to carry out
their attacks precisely or know the effects after attacks.

@@

In this work, we utilize the new features of \ac{USB} 3.x~\cite{usb31,usb32} to
address the problem above.  Benefiting from the latest protocol, we simulate
external display and thus obtain the video stream to perform accurate
attacks. However, we still unable to bypass defenses like GoodUSB~\cite{tian2015defending}, which completely blocks unauthorized functionality. This will be further discussed in Section~\ref{sec:discussion}

@@

%\fengwei{We need to
%explain the figure. What are the boxes? Where is victim? Where is the attacker?
%The list below only shows the internal components in the malicious \ac{USB} device.
%We might also consider to explain this in the Figure caption.}

@@

	\item\underline{USB 3.x Hub} exports the \ac{USB} 3.x connector into various ports, like DisplayPort, \ac{USB} 2.0 port, etc.

@@

	\item\underline{\ac{HID} Emulator} emulates \ac{HID} device which can be controlled from the attacker.

	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via \ac{HID} Emulator.

@@

\textbf{\ac{HID} Emulation Mode.} This mode majorly relies on the ``\ac{HID} Emulator'' in the Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such feedback channel largely strengthen the attack ability of \tool.

Moreover, as the mouse relies on the visual feedback to work properly, its
emulation and automation were not supported by the original version of BadUSB.
Yet with the video output support from \ac{USB} 3.x, our \tool implements a
full-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
programs and shows attacks in the mobile attack scenarios. Details can
be obtained in Section~\ref{sec:experiment}.

@@

\textbf{Video Capture Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of \ac{USB} 3.x; it uses
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

@@

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only
the victim's device treat \tool as an external display, but also a valid \ac{HID}
input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirect it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movement from the attacker
through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.

### 2021-03-07 WOOT/Files/conclusion.tex
fuck me with acronyms please

Leveraging the new features of USB 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The HID Emulation mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The full control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes and shows it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

>>>>

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The full control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes and shows it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

### 2021-03-07 WOOT/Files/countermeasure.tex
fuck me with acronyms please

\textbf{Distrust-by-Default.} Most security issues of USB protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
is worth mentioning that \textit{distrust-by-default} policy is not the same as
GoodUSB~\cite{tian2015defending}.  
%\fengwei{the following sentence needs to be
%written. I am confused.}\hongyi{Fixed, use more concise sentences} 
GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device. Though \textit{distrust-by-default} policy effectively
prevents these attacks, it also causes considerable inconvenience for users.

\textbf{Isolated UI Rendering.} During our experiments, we noticed that \tool
is actually unable to redirect out the locking screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the locking screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated UI Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated UI render layers and corresponding drivers, one
is secure the other is insecure. When an application requires to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both the trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive. Thus, the `password' and `keyboard' are not rendered on untrusted screen.
 \fengwei{we need more text to describe the figure}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated UI Rendering}%\shuqing{Maybe we can increase the font?}
	\label{fig:isolated_ui}
\end{figure}
%\fengwei{what are untrusted and trusted screens? are they internal and external displays?}
%\hongyi{Fixed by using the same term and additional description}

>>>>

\textbf{Distrust-by-Default.} Most security issues of \ac{USB} protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
is worth mentioning that \textit{distrust-by-default} policy is not the same as
GoodUSB~\cite{tian2015defending}.  
%\fengwei{the following sentence needs to be
%written. I am confused.}\hongyi{Fixed, use more concise sentences} 
GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device. Though \textit{distrust-by-default} policy effectively
prevents these attacks, it also causes considerable inconvenience for users.

\textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
is actually unable to redirect out the locking screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the locking screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated \ac{UI} Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
is secure the other is insecure. When an application requires to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both the trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive. Thus, the `password' and `keyboard' are not rendered on untrusted screen.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated \ac{UI} Rendering}%\shuqing{Maybe we can increase the font?}
	\label{fig:isolated_ui}
\end{figure}
%\fengwei{what are untrusted and trusted screens? are they internal and external displays?}
%\hongyi{Fixed by using the same term and additional description}

### 2021-03-07 WOOT/Files/discussion.tex
impl free of GoodUSB
fuck me with acronyms please

\subsection{Limitation}

There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the USB devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.

\subsection{Impact}

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The USB protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  Due to the neglect to
check the security of plugged-in USB devices of non-professional users, \tool
can be hardly detected by them while attacks are performing.  The popularity
and universality of public USB devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface, as well as control the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

>>>>

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. Depending on victim's settings, the \tool may be used as an extended monitor or not be enabled at all. Additionally, some smartphone vendor (e.g. Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring. In these cases, \tool is either easily noticeable to victim or disabled.  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connector does not support \ac{USB} 3.2 protocol. This lack of support further limited \tool.
\begin{comment}
There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the \ac{USB} devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.
\end{comment}
\subsection{Impact}

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The \ac{USB} protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  Due to the neglect to
check the security of plugged-in \ac{USB} devices of non-professional users, \tool
can be hardly detected by them while attacks are performing.  The popularity
and universality of public \ac{USB} devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface, as well as control the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.
